P.berghei pir analysis

### 2021-09-06 chapter3_results_bergheiPir/Manuscript_Github_Pberghei_pir.Rmd
density plots for berg and r fun for sourcing

@@

##Supp figure 1A - Pearson correlation plot of collated samples.

>>>>

## Density plots

```{r density_plots}
# Compute the average bandwidth for all the samples so that we have the same value for each figure.
list_bw = lapply(expt_tpms, function(expt){ 
  lapply(colnames(expt$tpm)[-1], 
         function(sample){
           data = as.numeric(unlist(select(expt$tpm, 
                                           paste(sample))))
           dens = density(log1p(data))
           dens$bw
         })
})
bw_mean = mean(unlist(list_bw))
bw_range = max(unlist(unlist(list_bw))) - min(unlist(unlist(list_bw)))
print(paste('Bandwidth range = ', bw_range))

source('../rfunctions/density_samples_fun.R')
lapply(expt_tpms, density_samples, save = TRUE)
```

@@

##Pearson correlation plot of collated samples.
